---
title: "Modelling Steps"
author: "Jonathan Maynard"
date: "May 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### The ecological site modeling framework consists of five steps: 
    1. Develop an ESG point dataset for training and cross-validation 
    2. Preprocess ESG covariates for tiling and point overlay
    3. Covariate feature selection and model development
    4. Spatial predictions using tiled raster stacks
    5. Model validation and uncertainty analysis 

#### Steps 1 and 2 were performed using the following R scripts: 
  * [**Covariate Processing**](https://jjmaynard.github.io/ESG.Mapping/ESG_Covariate_Processing.html)
  * [**Hyper-temporal RS-Image Processing**](https://jjmaynard.github.io/ESG.Mapping/ESG_HyperTemp_Image_Processing.html)

#### Steps 3 through 5 were performed using the following R scripts: 
  * [**Modeling, Prediction and Validation**](https://jjmaynard.github.io/ESG.Mapping/ESG_MLR_Modeling.html)
  * [**Mapping SSURGO ESGs**](https://jjmaynard.github.io/ESG.Mapping/ESG_SSURGO_mapping.html).
```{r include=FALSE}
library(png)
library(grid)
library(here)
img <- readPNG(here("docs", "ESG_Modeling_Framework.png"))
```
```{r fig.width=5, fig.height=8,echo=FALSE}
grid.raster(img)
```

