---
title: "ESG SSURGO Processing"
author: "Jonathan Maynard"
email: jonathan.maynard@ars.usda.gov
date: "Feb 10, 2017"
output: html_document
---

#### This notebook processes and plots SSURGO-derived ESG maps based on the ESG class associated with the dominant component within each soil map unit. SSURGO ecological site and SMU component data were downloaded from SoilDataAccess (Accessed 12 Oct. 2017), merged based on the representative component percentage for each SMU, and aggregated by dominant condition. In rare cases (<0.5%) where multiple ecological site concepts resulted in equal representative percentages within a SMU, ESD selection was based on consulting local soil survey office and analysis of correlated minor components. The ESD-ESG look-up tables developed by the Ecological Site Grouping workshops were then used to assign the appropriate ESG group to each SMU ecological site class. 

```{r eval=FALSE}
required.packages <- c("here", "doParallel", "foreach", "dplyr", "tidyr", 
    "soilDB", "rgeos", "sp", "raster", "maps", "rgdal", "sf", "ggplot2", 
    "rasterVis")
new.packages <- required.packages[!(required.packages %in% installed.packages()[, 
    "Package"])]
if (length(new.packages)) install.packages(new.packages)
lapply(required.packages, require, character.only = T)
rm(required.packages, new.packages)


no_cores <- detectCores() - 1
cl <- makeCluster(no_cores, type = "SOCK", outfile = "")
registerDoParallel(cl)
getDoParWorkers()
```

## Load in study boundaries and NASIS points
```{r eval=FALSE}
# Study areas
NM <- readOGR(dsn = "/data/data1/R_DATA/Imagery_Vector/Ecosite_Group_Mapping/Chihuahuan_study_area", 
    layer = "Chihauhuan_Study_Area_Boundary")
CO <- readOGR(dsn = "/data/data1/R_DATA/Imagery_Vector/Ecosite_Group_Mapping/CO_Plat_study_area", 
    layer = "epaL4_mlra35sel_bndc")
# Load in NASIS training points
co.points <- readOGR(dsn = "/data/data2/data/esgMapping/analysis/data/derived_data/vector_data", 
    layer = "CO_points_final")
nm.points <- readOGR(dsn = "/data/data2/data/esgMapping/analysis/data/derived_data/vector_data", 
    layer = "NM_points_final")
# ESG lookup key
unique(co.points@data[10:11])
unique(nm.points@data[14:15])
```

## Extract SSURGO spatial data for Chihuahuan Deseart study area using Soil Data Access (SDA)
```{r eval=FALSE}
# Read in MLRA 42 SMU list
mlra42_esg <- read.csv("/data/data2/mlra42-esg.csv")
SMU_list <- mlra42_esg$mukey

# set number of SMU per query to 50
x <- seq(1, length(SMU_list), 50)
y <- seq(50, length(SMU_list), 50)
y[length(y)] <- length(SMU_list)
x <- x[-length(x)]
# This works but throws an error when a very large SMU is present.
# Therefore requires limiting the number of SMUs, i.e., 2 or less
SMU_geo <- list()
SMU_geo <- foreach(i = 1:length(x), .packages = c("soilDB", "purrr")) %dopar% 
    {
        # for(i in 1:3){
        tryCatch({
            SMU_geo[[i]] <- SDA_query(paste0("select G.MupolygonWktWgs84 as geom, mapunit.mukey, muname
  FROM mapunit
    CROSS APPLY SDA_Get_MupolygonWktWgs84_from_Mukey(mapunit.mukey) as G
    WHERE mukey IN ('", 
                paste0(SMU_list[x[i]:y[i] - 1], sep = "', '", collapse = ""), 
                SMU_list[y[i]], "')"))
        }, error = function(e) {
            cat("ERROR :", conditionMessage(e), "\n")
        })
    }

SMU_geo.all <- bind_rows(SMU_geo)
saveRDS(SMU_geo.all, "MLRA_42_SMU1.rds")
length(unique(SMU_geo.all$mukey))
length(SMU_list)
missing <- match(SMU_list, unique(SMU_geo.all$mukey), nomatch = NA)
SMU_list_rerun <- SMU_list[which(is.na(missing))]
# rm(SMU_geo.all) set number of SMU per query to 1
x <- seq(1, length(SMU_list_rerun), 10)
y <- seq(10, length(SMU_list_rerun), 10)
y[length(y)] <- length(SMU_list_rerun)
x <- x[-length(x)]
# This works but throws an error when a very large SMU is present.
# Therefore requires limiting the number of SMUs, i.e., 2 or less
SMU_geo2 <- list()
SMU_geo2 <- foreach(i = 1:length(x), .packages = c("soilDB")) %dopar% {
    # for(i in 1:3){
    tryCatch({
        SMU_geo2[[i]] <- SDA_query(paste0("select G.MupolygonWktWgs84 as geom, mapunit.mukey, muname
      FROM mapunit
      CROSS APPLY SDA_Get_MupolygonWktWgs84_from_Mukey(mapunit.mukey) as G
      WHERE mukey IN ('", 
            paste0(SMU_list_rerun[x[i]:y[i] - 1], sep = "', '", collapse = ""), 
            SMU_list_rerun[y[i]], "')"))
    }, error = function(e) {
        cat("ERROR :", conditionMessage(e), "\n")
    })
}

# SMU_geo.all <- readRDS('SMU_geo_all1.rds')
SMU_geo.all <- bind_rows(SMU_geo.all, SMU_geo2)
saveRDS(SMU_geo.all, "MLRA_42_SMU2.rds")
missing2 <- match(SMU_list, unique(SMU_geo.all$mukey), nomatch = NA)
SMU_list_rerun2 <- SMU_list[which(is.na(missing2))]
# rm(SMU_geo.all)

x <- seq(1, length(SMU_list_rerun2), 1)
y <- seq(1, length(SMU_list_rerun2), 1)

SMU_geo3 <- list()
SMU_geo3 <- foreach(i = 1:length(SMU_list_rerun2), .packages = c("soilDB")) %dopar% 
    {
        # for(i in 1:3){
        tryCatch({
            SMU_geo3[[i]] <- SDA_query(paste0("select G.MupolygonWktWgs84 as geom, mapunit.mukey, muname
      FROM mapunit
      CROSS APPLY SDA_Get_MupolygonWktWgs84_from_Mukey(mapunit.mukey) as G
      WHERE mukey IN ('", 
                paste0(SMU_list_rerun2[x[i]:y[i] - 1], sep = "', '", collapse = ""), 
                SMU_list_rerun2[y[i]], "')"))
        }, error = function(e) {
            cat("ERROR :", conditionMessage(e), "\n")
        })
    }
# SMU_geo.all <- readRDS('SMU_geo_all2.rds')
SMU_geo.all <- bind_rows(SMU_geo.all, SMU_geo3)
saveRDS(SMU_geo.all, "MLRA_42_SMU2.rds")

mu.unique <- unique(SMU_geo.all$mukey)

save.image("SSURGO_MLRA_42.RData")
SMU_geo.proc <- processSDA_WKT(SMU_geo.all)

writeOGR(SMU_geo.proc, dsn = ".", layer = "SMU_geo.proc", driver = "ESRI Shapefile", 
    overwrite_layer = TRUE)

# Color palette used in rangelands article
cbPalette <- c("#00a884", "#beffe7", "#ffa77f", "#ffffbf", "#737301", "#fe0000", 
    "#0071fe", "#732500")

SMU_geo.proc.sf <- SMU_geo.proc %>% st_as_sf() %>% st_transform(st_crs(NM.sf))
SMU_geo.proc.sf$Area <- st_area(SMU_geo.proc.sf)

NM.sf <- NM %>% st_as_sf()
mlra42_ssurgo_esg <- SMU_geo.proc %>% st_as_sf() %>% st_transform(st_crs(NM.sf)) %>% 
    st_intersection(NM.sf) %>% left_join(mlra42_esg, by = "mukey")

mlra42_ssurgo_esg$GroupName = factor(mlra42_ssurgo_esg$GroupName, levels(mlra42_ssurgo_esg$GroupName)[c(7, 
    3, 6, 4, 1, 5, 2)])
st_write(mlra42_ssurgo_esg, "/data/data2/data/esgMapping/analysis/data/derived_data/SSURGO_ESG/mlra42_ssurgo_esg.shp")

mlra42_ssurgo_esg$Area <- st_area(mlra42_ssurgo_esg)
area <- mlra42_ssurgo_esg$Area
describe(data.frame(as.numeric(area)))
quantile(mlra42_ssurgo_esg$Area, c(0.99, 0.05, 0.01, 0.005))

sub <- SMU_geo.proc.sf %>% filter(Area < quantile(mlra42_ssurgo_esg$Area, 
    0.005))

# cbPalette <-
# c('#00a884','#beffe7','#ffa77f','#ffffbf','#737301','#fe0000','#0071fe','#732500')

# create fishnet grid to underlay polygon map make an object the size
# and shape of the output you want
NM.sf <- NM %>% st_as_sf()
NM_bb <- matrix(c(-1213894.1, 1307347.4, -737762.7, 1307347.4, -737762.7, 
    768173.3, -1213894.1, 768173.3, -1213894.1, 1307347.4), byrow = TRUE, 
    ncol = 2) %>% list() %>% st_polygon() %>% st_sfc(., crs = st_crs(NM.sf))

# Grid
NM_grid <- st_make_grid(NM_bb, n = c(60, 60), crs = st_crs(NM), what = "polygons") %>% 
    st_sf(geometry = ., data.frame(ID = 1:length(.))) %>% st_intersection(NM.sf)
plot(NM_grid)

cbPalette <- c("#8c510a", "#bf812d", "#dfc27d", "#f6e8c3", "#c7eae5", "#5ab4ac", 
    "#01665e")
mlra42_ssurgo_esg.plot <- ggplot() + geom_sf(data = NM_grid, fill = NA, 
    show.legend = F, color = "black", lwd = 0.4) + geom_sf(data = mlra42_ssurgo_esg, 
    aes(fill = factor(GroupName)), color = NA) + coord_sf(datum = st_crs(mlra42_ssurgo_esg)) + 
    labs(x = "Long", y = "Lat", fill = "ESG") + ggtitle("Ecological Site Group") + 
    scale_fill_manual(values = cbPalette)
# mlra42_ssurgo_esg.plot

ggsave(mlra42_ssurgo_esg.plot, file = "/data/data2/data/esgMapping/analysis/figures/NM_ssurgo_esg_plot.pdf", 
    width = 6, height = 6)
ggsave(mlra42_ssurgo_esg.plot, file = "/data/data2/data/esgMapping/analysis/figures/NM_ssurgo_esg_plot.png", 
    width = 6, height = 6, type = "cairo-png")


# MLRA SSURGO ESG
mlra35_ssurgo_esg <- st_read("/data/data2/data/esgMapping/analysis/data/derived_data/SSURGO_ESG/CO_Plat_SSURGO_ESGs/SSURGO_ESGs_UT_MLRA35.shp", 
    quiet = TRUE)
mlra35_ssurgo_esg$Name = factor(mlra35_ssurgo_esg$Name, levels(mlra35_ssurgo_esg$Name)[c(5, 
    6, 8, 7, 3, 4, 1, 2)])
mlra35_ssurgo_esg$Area <- st_area(mlra35_ssurgo_esg)
quantile(mlra35_ssurgo_esg$Area, c(0.99, 0.05, 0.01, 0.005))
summary(mlra35_ssurgo_esg$Area)
# make an object the size and shape of the output you want
CO.sf <- CO %>% st_as_sf()
CO_bb <- matrix(c(-1553413, 1952277, -1110609, 1952277, -1110609, 1629234, 
    -1553413, 1629234, -1553413, 1952277), byrow = TRUE, ncol = 2) %>% 
    list() %>% st_polygon() %>% st_sfc(., crs = st_crs(CO.sf))

# Grid
CO_grid <- st_make_grid(CO_bb, n = c(60, 60), crs = st_crs(CO), what = "polygons") %>% 
    st_sf(geometry = ., data.frame(ID = 1:length(.))) %>% st_intersection(CO.sf)
plot(CO_grid_
x10)
# palette for mlra 35 with factor levels: [1] 'Bottoms and flats',
# 'Deep rocky', 'Finer shrublands', 'Outcrops and slopes', 'Saline
# hills and badlands', 'Saline uplands and flats', 'Sandy grasslands
# and shrublands', 'Shallow shrublands and woodlands' cbPalette <-
# c('#0071fe','#732500','#737301','#fe0000','#00a884','#beffe7','#ffffbf','#ffa77f')
cbPalette <- c("#8c510a", "#bf812d", "#dfc27d", "#f6e8c3", "#c7eae5", "#80cdc1", 
    "#35978f", "#01665e")

mlra35_ssurgo_esg.plot <- ggplot() + geom_sf(data = CO_grid, fill = NA, 
    show.legend = F, color = "black", lwd = 0.4) + geom_sf(data = mlra35_ssurgo_esg, 
    aes(fill = factor(Name)), color = NA) + coord_sf(datum = st_crs(mlra35_ssurgo_esg)) + 
    labs(x = "Long", y = "Lat", fill = "ESG") + ggtitle("Ecological Site Group") + 
    scale_fill_manual(values = cbPalette)
# mlra35_ssurgo_esg.plot

ggsave(mlra35_ssurgo_esg.plot, file = "/data/data2/data/esgMapping/analysis/figures/CO_ssurgo_esg_plot.pdf", 
    width = 6, height = 6)
ggsave(mlra35_ssurgo_esg.plot, file = "/data/data2/data/esgMapping/analysis/figures/CO_ssurgo_esg_plot.png", 
    width = 6, height = 6, type = "cairo-png")


save.image("/data/data2/data/esgMapping/R/CO_NM_ESG_SSURGO.RData")
load("/data/data2/data/esgMapping/R/CO_NM_ESG_SSURGO.RData")

# Extract cross validation and external validation points from SSURGO
# polygons



CO.training.points <- st_as_sf(co.points) %>% dplyr::select(c("esdname", 
    "ESG_number", "ESG_Name", "ESG_ID"))
NM.training.points <- st_as_sf(nm.points) %>% dplyr::select(c("esd_unique", 
    "ESG", "Name"))
CO_Validation_Final <- st_read("/data/data2/data/esgMapping/analysis/data/derived_data/vector_data/CO_ext_valid_points.shp") %>% 
    st_transform(st_crs(CO.training.points)) %>% dplyr::select(c(ESG_number_val = "ESG_number", 
    esd_unique_val = "esd_unique"))
NM_Validation_Final <- st_read("/data/data2/data/esgMapping/analysis/data/derived_data/vector_data/NM_ext_valid_points.shp") %>% 
    st_transform(st_crs(NM.training.points)) %>% dplyr::select(ESG_number_val = "Group")
NM_Validation_Final <- NM_Validation_Final[-setdiff(seq(1:1427), nm.validation.points.covariates$Index), 
    ]
mlra35_ssurgo_esg.sf <- st_as_sf(mlra35_ssurgo_esg) %>% st_transform(st_crs(CO.training.points)) %>% 
    dplyr::select(c(esd_ssurgo = "esd_unique", ESG_ssurgo = "ESG", Name_ssurgo = "Name"))
mlra42_ssurgo_esg.sf <- st_as_sf(mlra42_ssurgo_esg) %>% st_transform(st_crs(NM.training.points)) %>% 
    dplyr::select(c(esd_ssurgo = "ecoclassname.x", ESG_ssurgo = "GroupID", 
        Name_ssurgo = "GroupName"))

# CO Training data
mlra35_ssurgo_esg_training_pts <- st_join(CO.training.points, mlra35_ssurgo_esg.sf, 
    join = st_intersects) %>% distinct()
mlra35_ssurgo_esg_training_pts <- mlra35_ssurgo_esg_training_pts[-897, 
    ]
mlra35_ssurgo_esg_training_pts <- mlra35_ssurgo_esg_training_pts %>% bind_cols(CO_dsm.ens.pred$data %>% 
    arrange(id) %>% select(ens_truth = "truth", ens_response = "response"))
mlra35_ssurgo_esg_training_pts$ESG_ssurgo[mlra35_ssurgo_esg_training_pts$ESG_ssurgo == 
    0] <- NA
mlra35_ssurgo_esg_training_pts <- na.omit(mlra35_ssurgo_esg_training_pts)
mlra35_ssurgo_esg_training_pts$ESG_ID_ssurgo <- as.factor(paste0("ES", 
    mlra35_ssurgo_esg_training_pts$ESG_ssurgo))
ACC(mlra35_ssurgo_esg_training_pts$ESG_ID, mlra35_ssurgo_esg_training_pts$ESG_ID_ssurgo)
ACC(mlra35_ssurgo_esg_training_pts$ESG_ID, mlra35_ssurgo_esg_training_pts$ens_response)
mlra35_ssurgo_esg_training_cfm <- caret::confusionMatrix(mlra35_ssurgo_esg_training_pts$ESG_ID, 
    mlra35_ssurgo_esg_training_pts$ESG_ID_ssurgo)
mlra35_ens_esg_training_cfm <- caret::confusionMatrix(mlra35_ssurgo_esg_training_pts$ens_response, 
    mlra35_ssurgo_esg_training_pts$ESG_ID)

# External validation data
mlra35_ssurgo_esg_extVal_pts <- st_join(CO_Validation_Final, mlra35_ssurgo_esg.sf, 
    join = st_intersects) %>% distinct()
mlra35_ssurgo_esg_extVal_pts <- mlra35_ssurgo_esg_extVal_pts %>% bind_cols(CO_dsm_ens_extVal$data %>% 
    select(ens_response = "response"))
mlra35_ssurgo_esg_extVal_pts$ESG_ssurgo[mlra35_ssurgo_esg_extVal_pts$ESG_ssurgo == 
    0] <- NA
mlra35_ssurgo_esg_extVal_pts <- na.omit(mlra35_ssurgo_esg_extVal_pts)
mlra35_ssurgo_esg_extVal_pts$ESG_ID_ssurgo <- as.factor(paste0("ES", mlra35_ssurgo_esg_extVal_pts$ESG_ssurgo))
mlra35_ssurgo_esg_extVal_pts$ESG_number_val <- as.factor(paste0("ES", mlra35_ssurgo_esg_extVal_pts$ESG_number_val))
levels(mlra35_ssurgo_esg_extVal_pts$ESG_ID_ssurgo) <- c(levels(mlra35_ssurgo_esg_extVal_pts$ESG_ID_ssurgo), 
    "ES1", "ES2", "ES99")
levels(mlra35_ssurgo_esg_extVal_pts$ESG_number_val) <- c(levels(mlra35_ssurgo_esg_extVal_pts$ESG_number_val), 
    "ES1", "ES6")
ACC(mlra35_ssurgo_esg_extVal_pts$ESG_number_val, mlra35_ssurgo_esg_extVal_pts$ESG_ID_ssurgo)
ACC(mlra35_ssurgo_esg_extVal_pts$ESG_number_val, mlra35_ssurgo_esg_extVal_pts$ens_response)
mlra35_ssurgo_esg_exVal_cfm <- caret::confusionMatrix(mlra35_ssurgo_esg_extVal_pts$ESG_ID_ssurgo, 
    mlra35_ssurgo_esg_extVal_pts$ESG_number_val)
mlra35_ens_esg_exVal_cfm <- caret::confusionMatrix(mlra35_ssurgo_esg_extVal_pts$ens_response, 
    mlra35_ssurgo_esg_extVal_pts$ESG_number_val)

CO_training_cfm <- bind_cols(data.frame(mlra35_ssurgo_esg_training_cfm$byClass) %>% 
    select(c(PA_ssurgo_training = "Sensitivity", UA_ssurgo_training = "Pos.Pred.Value")), 
    data.frame(mlra35_ens_esg_training_cfm$byClass) %>% select(c(PA_ens_training = "Sensitivity", 
        UA_ens_training = "Pos.Pred.Value")))

CO_exVal_cfm <- bind_cols(data.frame(mlra35_ssurgo_esg_exVal_cfm$byClass) %>% 
    select(c(PA_ssurgo_exVal = "Sensitivity", UA_ssurgo_exVal = "Pos.Pred.Value")), 
    data.frame(mlra35_ens_esg_exVal_cfm$byClass) %>% select(c(PA_ens_exVal = "Sensitivity", 
        UA_ens_exVal = "Pos.Pred.Value")))

CO_ssurgo_ens_cfm <- bind_cols(CO_training_cfm, CO_exVal_cfm)

mlra35_ssurgo_esg_training_cfm$overall
mlra35_ens_esg_training_cfm$overall
mlra35_ssurgo_esg_exVal_cfm$overall
mlra35_ens_esg_exVal_cfm$overall

# NM Training data
mlra42_ssurgo_esg_training_pts <- st_join(NM.training.points, mlra42_ssurgo_esg.sf, 
    join = st_intersects) %>% distinct()
mlra42_ssurgo_esg_training_pts <- mlra42_ssurgo_esg_training_pts[-setdiff(seq(1:2626), 
    nm.points.covariates$Index), ]
mlra42_ssurgo_esg_training_pts <- mlra42_ssurgo_esg_training_pts %>% bind_cols(NM_dsm.ens.pred$data %>% 
    arrange(id) %>% select(ens_truth = "truth", ens_response = "response"))
mlra42_ssurgo_esg_training_pts$ESG_ssurgo[mlra42_ssurgo_esg_training_pts$ESG_ssurgo == 
    0] <- NA
mlra42_ssurgo_esg_training_pts <- na.omit(mlra42_ssurgo_esg_training_pts)
mlra42_ssurgo_esg_training_pts$ESG_ID_ssurgo <- as.factor(paste0("ES", 
    mlra42_ssurgo_esg_training_pts$ESG_ssurgo))
ACC(mlra42_ssurgo_esg_training_pts$ESG_ID, mlra42_ssurgo_esg_training_pts$ESG_ID_ssurgo)
ACC(mlra42_ssurgo_esg_training_pts$ESG_ID, mlra42_ssurgo_esg_training_pts$ens_response)
mlra42_ssurgo_esg_training_cfm <- caret::confusionMatrix(mlra42_ssurgo_esg_training_pts$ESG_ID_ssurgo, 
    mlra42_ssurgo_esg_training_pts$ESG_ID)
mlra42_ens_esg_training_cfm <- caret::confusionMatrix(mlra42_ssurgo_esg_training_pts$ens_response, 
    mlra42_ssurgo_esg_training_pts$ESG_ID)

# External validation data
NM_Validation_Final <- NM_Validation_Final %>% bind_cols(NM_dsm_ens_extVal$data %>% 
    select(ens_response = "response"))
mlra42_ssurgo_esg_extVal_pts <- st_join(NM_Validation_Final, mlra42_ssurgo_esg.sf, 
    join = st_intersects) %>% distinct()
NM_Validation_Final %>% distinct(geometry, .keep_all = TRUE)
mlra42_ssurgo_esg_extVal_pts$ESG_ssurgo[mlra42_ssurgo_esg_extVal_pts$ESG_ssurgo == 
    0] <- NA
mlra42_ssurgo_esg_extVal_pts <- na.omit(mlra42_ssurgo_esg_extVal_pts)
mlra42_ssurgo_esg_extVal_pts$ESG_ID_ssurgo <- as.factor(paste0("ES", mlra42_ssurgo_esg_extVal_pts$ESG_ssurgo))
mlra42_ssurgo_esg_extVal_pts$ESG_number_val <- as.factor(paste0("ES", mlra42_ssurgo_esg_extVal_pts$ESG_number_val))
ACC(mlra42_ssurgo_esg_extVal_pts$ESG_number_val, mlra42_ssurgo_esg_extVal_pts$ESG_ID_ssurgo)
ACC(mlra42_ssurgo_esg_extVal_pts$ESG_number_val, mlra42_ssurgo_esg_extVal_pts$ens_response)
mlra42_ssurgo_esg_exVal_cfm <- caret::confusionMatrix(mlra42_ssurgo_esg_extVal_pts$ESG_ID_ssurgo, 
    mlra42_ssurgo_esg_extVal_pts$ESG_number_val)
mlra42_ens_esg_exVal_cfm <- caret::confusionMatrix(mlra42_ssurgo_esg_extVal_pts$ens_response, 
    mlra42_ssurgo_esg_extVal_pts$ESG_number_val)

NM_training_cfm <- bind_cols(data.frame(mlra42_ssurgo_esg_training_cfm$byClass) %>% 
    select(c(PA_ssurgo_training = "Sensitivity", UA_ssurgo_training = "Pos.Pred.Value")), 
    data.frame(mlra42_ens_esg_training_cfm$byClass) %>% select(c(PA_ens_training = "Sensitivity", 
        UA_ens_training = "Pos.Pred.Value")))

NM_exVal_cfm <- bind_cols(data.frame(mlra42_ssurgo_esg_exVal_cfm$byClass) %>% 
    select(c(PA_ssurgo_exVal = "Sensitivity", UA_ssurgo_exVal = "Pos.Pred.Value")), 
    data.frame(mlra42_ens_esg_exVal_cfm$byClass) %>% select(c(PA_ens_exVal = "Sensitivity", 
        UA_ens_exVal = "Pos.Pred.Value")))

NM_ssurgo_ens_cfm <- bind_cols(NM_training_cfm, NM_exVal_cfm)

mlra42_ssurgo_esg_training_cfm$overall
mlra42_ens_esg_training_cfm$overall
mlra42_ssurgo_esg_exVal_cfm$overall
mlra42_ens_esg_exVal_cfm$overall
# Calculate qunatity and allocation dissagreement

CO_training_ssurgo.kstat <- kstat(mlra35_ssurgo_esg_training_pts$ESG_ID_ssurgo, 
    mlra35_ssurgo_esg_training_pts$ESG_ID)
CO_training_dsm_ens.kstat <- kstat(mlra35_ssurgo_esg_training_pts$ens_response, 
    mlra35_ssurgo_esg_training_pts$ESG_ID)
CO_extVal_ssurgo.kstat <- kstat(mlra35_ssurgo_esg_extVal_pts$ESG_ID_ssurgo, 
    mlra35_ssurgo_esg_extVal_pts$ESG_number_val)
CO_extVal__dsm_ens.kstat <- kstat(mlra35_ssurgo_esg_extVal_pts$ens_response, 
    mlra35_ssurgo_esg_extVal_pts$ESG_number_val)

NM_training_ssurgo.kstat <- kstat(mlra42_ssurgo_esg_training_pts$ESG_ID_ssurgo, 
    mlra42_ssurgo_esg_training_pts$ESG_ID)
NM_training_dsm_ens.kstat <- kstat(mlra42_ssurgo_esg_training_pts$ens_response, 
    mlra42_ssurgo_esg_training_pts$ESG_ID)
NM_extVal_ssurgo.kstat <- kstat(mlra42_ssurgo_esg_extVal_pts$ESG_ID_ssurgo, 
    mlra42_ssurgo_esg_extVal_pts$ESG_number_val)
NM_extVal__dsm_ens.kstat <- kstat(mlra42_ssurgo_esg_extVal_pts$ens_response, 
    mlra42_ssurgo_esg_extVal_pts$ESG_number_val)
#--------------------------------------------------------------------------------------------------------------------------------------

# Output data
save(SMU_geo.all, SMU_geo.proc, SMU_geo, SMU_geo2, SMU_geo3, SMU_geo.proc.sf, 
    SMU_geo.proc.sf.t, file = "/data/data2/data/esgMapping/R/SSURGO_SMU.Rdata")
```

